DESIGN OF A TWO-PIECE BRASSIERE CUP TO FIT BREAST DATA POINTS TOWARD ITS AUTOMATION

### 2020-11-25 template/paper/paper_e.tex
CommitFinalBeforeAlign

%Authors: Please do not make any changes on the commands below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[E]{scitrans}
%\usepackage{graphicx}
\usepackage{color}
\usepackage{math}
\usepackage{bm}
%\usepackage[dvipdfmx]{graphicx,xcolor}
\usepackage[dvipdfmx]{epsfig}
%
\appearyear{0000}
\vol{0}
\numberinvol{0}
\setcounter{page}{1}
\setcounter{volumepage}{1}
\Transaction
%%\Shortpaper
\ForSubmission
%Authors: Please do not make any changes on the commands above.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Developable surfaces can be unfolded into a plane without expanding or contracting. They are widely used in many industries from shipbuilding to manufacturing of clothing because they can represent surfaces made of leather, paper, or sheet metal. It is important to design two-dimensional (2D) shapes that form the required three-dimensional (3D) shape by bending and joining. In this paper, we focus on production of brassieres, which is related to design of two-dimensional shapes of plates. 
Brassieres are manufactured to meet various demands, such as to Herein we focus on the production of brassieres, which is related to the design of 2D shapes of plates. Brassieres are manufactured to meet various demands such as enhancing a woman’s breast size, creating cleavage, or minimizing breast movement. Due to these diverse demands, the cup shape is a critical element when designing a brassiere. A brassiere cup is formed by several pieces of cloth called patterns and a wire. Figure 1 shows an example of a two-piece brassiere cup composed of an upper pattern, lower pattern, and lower line. 
\begin{figure}[h!]
	\centering
	\subfigure[upper pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.eps}
		\label{fig:pattern_U}
	}
	\hfil
	\subfigure[lower pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.eps}
		\label{fig:pattern_L}
	}
	\\
	\subfigure[lower line]{
		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.eps}
		\label{fig:Wire}
	}
	\caption{Parts of a two-piece brassiere cup}
	\label{fig:patterns}
\end{figure}
 The three resulting curves are important to the design. The wire line corresponds to the boundary between the breast and body (\rfig{fig:TwoCurves}). The ridge line of the cup corresponds to the outline of a bust on a transverse plane, while the upper line connects the cup to the shoulder strap.

%==============================================================%
In apparel industries, the form of a product is fixed by fashion designers and pattern makers. Fashion designers draw the product image, while pattern makers determine the pattern shapes to meet various demands of the ideal shape.
%%fig
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.25]{./figure/Lines.eps}
	\caption{Expression of a wire line, a ridge line and an upper line}
	\label{fig:TwoCurves}
\end{figure}
\rfig{fig:process} overviews the design process of a brassiere cup. Pattern makers first consider the functional requirement of a brassiere cup based on the breast shape, and then they determine the pattern shape. This design process is based on experience and intuition. Hence, pattern makers must verify the shapes with a paper model of the cup and repeatedly modify the shapes to realize the intended function. This process may cause unnecessary repetition. To improve the design efficiency of brassieres, trial and error should be minimized. Herein we strive to automate the steps indicated by the dotted line in \rfig{fig:process}. 
A previous study on the influence of design on the function of a brassiere cup found that fitting the breast has the largest impact\cite{c1}. Hence, this study proposes a method to design the pattern shapes of a brassiere cup to fit the given breast shape. Here, the given 3D breast shape is assumed to be a cloud of data points, which can be obtained easily by measurements.

\begin{figure}[h!]
	\centering
	\includegraphics[width= 1.0 \columnwidth]{./figure/DesignProcess2.eps}
	\caption{Design process of a brassiere cup}
	\label{fig:process}
\end{figure}

@@

\chcolor{In a study to approximate developable surface, Yang et al. proposed a method to approximate surface with meshes composed of planar quadrilaterals\cite{cX1} and Odeo et al. proposed a method to define the developability of triangle meshes and appoximate them by a set of developable surfaces\cite{cX2}, and Martin et al. proposed a method to reconstruct surfaces by curved forming\cite{cX3}. But all of them only focus on approximating surface by developable surface, which means that they do not refer to the condition of a developable surface itself. When designing a brassiere, it is required to satisfy some conditons of a brassiere cup that designers intend.}

In a study on brassieres, Wakamatsu et al. proposed a method to predict the 3D shape of a paper cup model when the 2D shape of a pattern is given\cite{c10,c11}. Hence, patterns can be evaluated without actually creating a paper model. However, repetitive modification of the pattern is still required to obtain the target 3D shape of the cup. Ito et al. developed a paper model CAD system based on the theory of developable surfaces\cite{c12}. If a 3D curve, which means a sewn curve, and a 2D curve, which means a piece to be sewn, are given, this system can identify the feasible region where the sewn surface does not intersect itself. Unfortunately, it is difficult to design the pattern shapes. That is, determining the shape of 2D curves is challenging with this system. 
We previously proposed a method to design the pattern shape and its developable surface from two lines: a wire line and a ridge line. These lines are obtained by solving the optimization problem when the design parameters are the geodesic curvatures of a pattern shape and the objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line. However, the previously proposed method requires an iterative process to solve the optimization problem for the intended shape\cite{c13}, which is time-consuming.
Brassiere patterns are typically comprised of two or three pieces. Herein we focus on a two-piece brassiere cup, and we propose a design method to improve the design efficiency when a cloud of its data points is given.

@@

\begin{figure}[thpb]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Object_Coordinates.eps}
	\caption{Object coordinate system on the surface}
	\label{fig:obj_coord}
\end{figure}

@@

Here, the coefficients of the first fundamental form are represented as
\begin{equation}
E = \zetavec \cdot \zetavec = 1, F = \zetavec \cdot \xivec = 0, G = \xivec \cdot \xivec = 1.
\end{equation}
In addition, the coefficients of the second fundamental form are represented as
\begin{equation}
L = \zetavec' \cdot \eta = -\omega_{\xi}, M = \xivec' \cdot \eta = -\omega_{\zeta}.
\end{equation}
Then Gaussian curvature $K$ and the mean curvature $H$ are described by the following equations

@@

Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as
\begin{equation}
\Delta \mbold{g} = -\zetavec_a \Delta s_a + \zetavec_b \Delta s_b,
\end{equation}
where $ \zetavec_a$ and $\zetavec_b $ are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, respectively. Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ (\rfig{fig:Theta}). When the ruled surface is a developable surface, the plane $ \Theta $ is a tangent plane without twisting. Therefore, it leads to following equation:
\begin{equation}
\det (\zetavec_a, \mbold{g}, \mbold{g}+\Delta \mbold{g})=0
\label{eq:det_developeq}
\end{equation}
Solving \req{eq:det_developeq} gives
\begin{equation}
\det (\zetavec_a, \zetavec_b, \mbold{g})=0
\label{eq:Cond1}
\end{equation}
\begin{figure}[!h]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Theta.eps}
	\caption{Definition of $ \Theta $}
	\label{fig:Theta}
\end{figure}
\req{eq:Cond1} indicates that the arc length of each curve is subordination. When two curves are corresponded to edge lines and $s_b$ can be expressed as $s_b(s_a)$, $\mbold{d}_{\min}\equiv\frac{\mbold{g}}{|\mbold{g}|}$ is established. Then, a rib angle is calculated by \req{eq:d1d2_eq} as follows:
\begin{equation}
\alpha = -\sin^{-1}\left( \mbold{d}_{\min} \cdot \zetavec_a \right).
\end{equation}
Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as
\begin{equation}\label{eq:omegaVec}
\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha \end{array}\right] 
\end{equation}
Therefore, when two curves that lie on the surface are given, a developable surface can be determined.

@@

First, using \req{eq:d_mindoteq,eq:d_maxdoteq,eq:t*_eq}, the nearest surface parameters $ (s_w^*, t_w^*) $ of the lower cup to the point $ \mbold{p}_k $ can be derived. Then, the nearest point $ \mbold{X}(s^*, t^*) $ on the lower cup surface to the point $ \mbold{p}_k $ can be derived. Let $ t_{\max}=|\mbold{x}_R (s_r (s_w^* ))-\mbold{x}_W (s_w^* )| $ be the length of a generatrix on the wire line. If $ t_{\max} > t_w^*(s_w^*) $, that is, if the perpendicular projection point of the point $ \mbold{p}_k $ to the surface $ S_L $ is included in the lower cup, the point $ \mbold{p}_k $ is classified to the set $ D_L $. Otherwise, it is classified to the set $ D_U $. 
\begin{figure}[thpb]
	\centering
	\subfigure[$ t^*\leq t_{\max} $]{
		\includegraphics[width=0.45\columnwidth]{./figure/NotExceeding.eps}
		\label{fig:inD_L}
	}
	\hfil
	\subfigure[$ t^* > t_{\max} $]{
		\includegraphics[width=0.45\columnwidth]{./figure/Exceeding.eps}
		\label{fig:inD_U}
	}
	\caption{Relationship between $ t^*$ and $t_{\max}$.}
	\label{fig:which_in}
\end{figure}

@@

To guarantee that $ S_L $ and $ S_U $  are developable surfaces, the following equations must be satisfied 
\begin{equation}\label{eq:conds_DevSur1}
	\int_{0}^{L_L} \det (\zetavec_R(s_r(s_w)), \zetavec_W(s_w), \mbold{g}) ds_w = 0,
\end{equation}
\begin{equation}\label{eq:conds_DevSur2}
	\int_{0}^{L_L} \det (\zetavec_U(s_u(s_w)), \zetavec_W(s_w), \mbold{g}) ds_w = 0.
\end{equation}
Next, consider a “fuzzy” condition for a brassiere cup. The upper line has a point where it is connected with the shoulder strap. Hereafter, this point is called the connection point. 
\begin{figure}[!h]
	\centering
	\includegraphics[width = 0.7\columnwidth]{./figure/Connection_Point.eps}
	\caption{Expression about the connection point of a brassiere cup}
	\label{fig:aboutCP}
\end{figure}
Typically, this point is given as a fuzzy condition in the design process. This can lead to an unexpected error in the optimization problem. Therefore, we propose the following equation to deal with this fuzzy condition $ y \simeq Y $:
\begin{equation}\label{eq:FuzzyEq}
C(y,Y) = k_1 \exp( k_2(y-Y)^2 )
\end{equation}
where $ k_1 $ and $ k_2 $ are the variables to adjust the range that satisfies this condition. By adding this equation to the objective function, the fuzzy condition can be handled. Here, we assume that the position $ \mbold{X}_C $ to connect the upper line and the shoulder strap is given. Then the objective function $ V $ is described as
\begin{equation}\label{eq:ObjectFunc}
V = \Lambda(\mbold{D}) + \sum_{i=0}^{2} C(\mbold{x}_U \cdot \mbold{e}_i , \mbold{X}_C \cdot \mbold{e}_i)
\end{equation}
where $\mbold{e}_0 $ ,$\mbold{e}_1 $ and $\mbold{e}_2 $ are represented as unit vectors of $ x $,$ y $ and $ z $-axis. Solving this optimization under these constraints can provide the shape of the brassiere cup to fit the data points of a breast.

@@

\begin{equation}\label{eq:U_eq}
\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\omega_{\eta_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\upsilon_U} \cdot  \mbold{e}(s_w)  \end{array} \right]
\end{equation}
where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods. Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system.

From above, the objective function, which is expressed as \req{eq:ObjectFunc}, and the geometric constraints, which are expressed as  \req{eq:conds_endp1,eq:conds_endp2,eq:conds_DevSur1,eq:conds_DevSur2} are described by the following total parameter vector 
\begin{equation}\label{eq:TotalCoefs}
\mbold{a}_{\mathrm{all}} = \left[ \begin{array}{cccc}
\mbold{a}_R & \mbold{a}_U & \mbold{\Phi}_{R0} &\mbold{\Phi}_{U0} 
\end{array}\right].
\end{equation}

@@

\section*{SIMULATION AND VERIFICATION}
To demonstrate the utility of our method, we conducted simulations and a verification. For the verification, the infinitesimal rotational ratios vector   of the wire line is given as
\begin{equation}\label{eq:vrf_omgW}
\mbold{\omega}_W = \left[ \begin{array}{ccc}
0 & 2.91 & 0
\end{array}\right]^\mathrm{T}, 
\end{equation}
while the connection point $ \mbold{X}_C $ is given as 
\begin{equation}\label{eq:givenXc}
\mbold{X}_C = \left[ \begin{array}{ccc}
0 & 0.34 & 0.34
\end{array}\right]^\mathrm{T}.
\end{equation}
We prepared three examples of the simulation. Case (1) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}. Case (2) is a point cloud on a sphere whose radius is set on R by a uniform random number. \chcolor{Case (3) is a point cloud on a measured shape of a torso, which is a representative breast shape.}
The simulations aim to confirm that the propose method recreates a given shape and to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast”.

\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line. Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.  \rfig{fig:ObtainedSurfaceNDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively. 
Next, a uniform random number was generated by numpy.random() of Python. \rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2), \chcolor{and \rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data for Case (3) Table \ref{tbl:error and calc} shows the error and calculation time of each case. }

\chcolor{From the result of case(1), we confirm that our proposed method can recreate a given shape as a two-piece brassire cup. And From the result of case(2) and (3), we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.}

Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.
\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|c|c|} \hline
		& Error & Time[sec] \\ \hline
		case(1) & 0.10 & 1802 \\ \hline
		case(2) & 0.12 & 740 \\ \hline
		case(3) & 1.04& 1682 \\ \hline
	\end{tabular}
	\caption{The error and calculation time of our proposed method in each case.}
	\label{tbl:error and calc}
\end{table}

\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.eps}
		\label{fig:zx-NDS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.eps}
		\label{fig:zy-NDS}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.eps}
		\label{fig:xy-NDS}
	}
	\caption{Obtained shape and input data points in Case(1)}
	\label{fig:ObtainedSurfaceNDS}
\end{figure}

\begin{figure}[h!]
	\centering
	\subfigure[LOWER PATTERN]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternL.eps}
		\label{fig:low-NDS}
	}
	\hfil
	\subfigure[UPPER PATTERN]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedPatternU.eps}
		\label{fig:upp-NDS}
	}

	\caption{Obtained patterns in Case(1)}
	\label{fig:ObtainedSurfaceNDS_Pat}
\end{figure}

>>>>

%Authors: Please do not make any changes on the commands below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[E]{scitrans}
%\usepackage{graphicx}
\usepackage{color}
\usepackage{math}
\usepackage{bm}
\usepackage{here}
%\usepackage[dvipdfmx]{graphicx,xcolor}
\usepackage[dvipdfmx]{epsfig}
%
\appearyear{0000}
\vol{0}
\numberinvol{0}
\setcounter{page}{1}
\setcounter{volumepage}{1}
\Transaction
%%\Shortpaper
\ForSubmission
%Authors: Please do not make any changes on the commands above.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Developable surfaces can be unfolded into a plane without expanding or contracting. They are widely used in many industries from shipbuilding to manufacturing of clothing because they can represent surfaces made of leather, paper, or sheet metal. It is important to design two-dimensional (2D) shapes that form the required three-dimensional (3D) shape by bending and joining. In this paper, we focus on production of brassieres, which is related to design of two-dimensional shapes of plates. 
Brassieres are manufactured to meet various demands, such as to Herein we focus on the production of brassieres, which is related to the design of 2D shapes of plates. Brassieres are manufactured to meet various demands such as enhancing a woman’s breast size, creating cleavage, or minimizing breast movement. Due to these diverse demands, the cup shape is a critical element when designing a brassiere. A brassiere cup is formed by several pieces of cloth called patterns and a wire. Figure 1 shows an example of a two-piece brassiere cup composed of an upper pattern, lower pattern, and lower line. 
\begin{figure}[h!]
	\centering
	\subfigure[upper pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.png}
		\label{fig:pattern_U}
	}
	\hfil
	\subfigure[lower pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.png}
		\label{fig:pattern_L}
	}
	\\
	\subfigure[lower line]{
		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.png}
		\label{fig:Wire}
	}
	\caption{Parts of a two-piece brassiere cup}
	\label{fig:patterns}
\end{figure}
 The three resulting curves are important to the design. The wire line corresponds to the boundary between the breast and body (\rfig{fig:TwoCurves}). The ridge line of the cup corresponds to the outline of a bust on a transverse plane, while the upper line connects the cup to the shoulder strap.

%==============================================================%
In apparel industries, the form of a product is fixed by fashion designers and pattern makers. Fashion designers draw the product image, while pattern makers determine the pattern shapes to meet various demands of the ideal shape.
%%fig
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.25]{./figure/Lines.png}
	\caption{Expression of a wire line, a ridge line and an upper line}
	\label{fig:TwoCurves}
\end{figure}
\rfig{fig:process} overviews the design process of a brassiere cup. Pattern makers first consider the functional requirement of a brassiere cup based on the breast shape, and then they determine the pattern shape. This design process is based on experience and intuition. Hence, pattern makers must verify the shapes with a paper model of the cup and repeatedly modify the shapes to realize the intended function. This process may cause unnecessary repetition. To improve the design efficiency of brassieres, trial and error should be minimized. Herein we strive to automate the steps indicated by the dotted line in \rfig{fig:process}. 
A previous study on the influence of design on the function of a brassiere cup found that fitting the breast has the largest impact\cite{c1}. Hence, this study proposes a method to design the pattern shapes of a brassiere cup to fit the given breast shape. Here, the given 3D breast shape is assumed to be a cloud of data points, which can be obtained easily by measurements.

\begin{figure}[h!]
	\centering
	\includegraphics[width= 1.0 \columnwidth]{./figure/DesignProcess3.png}
	\caption{Design process of a brassiere cup}
	\label{fig:process}
\end{figure}

@@

\chcolor{In a study to approximate developable surface, Yang et al. proposed a method to approximate surface with meshes composed of planar quadrilaterals\cite{cX1} and Odeo et al. proposed a method to define the developability of triangle meshes and appoximate them by a set of developable surfaces\cite{cX2}, and Martin et al. proposed a method to reconstruct surfaces by curved forming\cite{cX3}. But all of them only focus on approximating surface by developable surface, which means that they do not refer to the condition of a developable surface itself. In designing a brassire cup, it is required not only to fit a breast shape but also to satisfy some conditions. For example, the upper line has a point where it is connected with the shoulder strap. Hereafter, this point is called the connection point as shown in \rfig{fig:aboutCP}.} 
\begin{figure}[!h]
		\centering
		\includegraphics[width = 0.7\columnwidth]{./figure/Connection_Point.png}
		\caption{Expression about the connection point of a brassiere cup}
		\label{fig:aboutCP}
\end{figure}

In a study on brassieres, Wakamatsu et al. proposed a method to predict the 3D shape of a paper cup model when the 2D shape of a pattern is given\cite{c10,c11}. Hence, patterns can be evaluated without actually creating a paper model. However, repetitive modification of the pattern is still required to obtain the target 3D shape of the cup. Ito et al. developed a paper model CAD system based on the theory of developable surfaces\cite{c12}. If a 3D curve, which means a sewn curve, and a 2D curve, which means a piece to be sewn, are given, this system can identify the feasible region where the sewn surface does not intersect itself. Unfortunately, it is difficult to design the pattern shapes. That is, determining the shape of 2D curves is challenging with this system. 
We previously proposed a method to design the pattern shape and its developable surface from two lines: a wire line and a ridge line. These lines are obtained by solving the optimization problem when the design parameters are the geodesic curvatures of a pattern shape and the objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line. However, the previously proposed method requires an iterative process to solve the optimization problem for the intended shape\cite{MyRef,MyRef2}, which is time-consuming.
Brassiere patterns are typically comprised of two or three pieces. Herein we focus on a two-piece brassiere cup, and we propose a design method to improve the design efficiency when a cloud of its data points is given.

@@

\begin{figure}[thpb]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Object_Coordinates.png}
	\caption{Object coordinate system on the surface}
	\label{fig:obj_coord}
\end{figure}

@@

Based on the theory of surface, the coefficients of the first fundamental form are represented as
\begin{equation}
E = \zetavec \cdot \zetavec = 1, F = \zetavec \cdot \xivec = 0, G = \xivec \cdot \xivec = 1.
\end{equation}
In addition, the coefficients of the second fundamental form are represented as
\begin{equation}
L = \zetavec' \cdot \etavec = -\omega_{\xi}, M = \xivec' \cdot \etavec = -\omega_{\zeta}.
\end{equation}
Then Gaussian curvature $K$ and the mean curvature $H$ are described by the following equations

@@

Note that $s_a$ can take an arbitrary value against $ s_b $. From \cite{MyRef2}, $ \zetavec_a$ and $\zetavec_b $, which are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, and $ \mbold{g} $ satisfy the following equation:
\begin{equation}
	\det (\zetavec_a, \zetavec_b, \mbold{g})=0. 
	\label{eq:Cond1}
\end{equation}
\req{eq:Cond1} indicates that the arc length of each curve is subordination, When two curves are corresponded to edge lines and $ s_b $ can be expressed as $s_b(s_a)$, $ \mbold{d}_{\min}  = \frac{\mbold{g}}{|\mbold{g}|}$ established. Then, a rib angle is calculated by \req{eq:d1d2_eq} as follows:
\begin{equation}\label{eq:alphaEq}
	\alpha_a = \sin^{-1} \mbold{d}_{\min} \cdot \zeta_a
\end{equation}
Then, using $ \mbold{d}_{\min} $ and $\alpha $, $ \mbold{\omega} $ can be represented as
\begin{equation}\label{eq:omegaVec}
\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha_a \end{array}\right] 
\end{equation}
Therefore, when two curves that lie on the surface are given, a developable surface can be determined.

@@

First, using \req{eq:d_mindoteq,eq:d_maxdoteq,eq:t*_eq}, the nearest surface parameters $ (s_w^*, t_w^*) $ of the lower cup to the point $ \mbold{p}_k $ can be derived. Then, the nearest point $ \mbold{X}(s^*, t^*) $ on the lower cup surface to the point $ \mbold{p}_k $ can be derived. Let $ t_{\max}=|\mbold{x}_R (s_r (s_w^* ))-\mbold{x}_W (s_w^* )| $ be the length of a generatrix on the wire line. If $ t_{\max} > t_w^*(s_w^*) $, that is, if the perpendicular projection point of the point $ \mbold{p}_k $ to the surface $ S_L $ is included in the lower cup, the point $ \mbold{p}_k $ is classified to the set $ D_L $. Otherwise, it is classified to the set $ D_U $. 
\begin{figure}[thpb]
	\centering
	\subfigure[$ t^*\leq t_{\max} $]{
		\includegraphics[width=0.45\columnwidth]{./figure/NotExceeding.png}
		\label{fig:inD_L}
	}
	\hfil
	\subfigure[$ t^* > t_{\max} $]{
		\includegraphics[width=0.45\columnwidth]{./figure/Exceeding.png}
		\label{fig:inD_U}
	}
	\caption{Relationship between $ t^*$ and $t_{\max}$.}
	\label{fig:which_in}
\end{figure}

@@

To guarantee that $ S_L $ and $ S_U $  are developable surfaces, the following equations must be satisfied 
\begin{equation}\label{eq:conds_DevSur1}
	\int_{0}^{L_L} \det (\zetavec_R(s_r(s_w)), \zetavec_W(s_w), \mbold{g}) ds_w = 0,
\end{equation}
\begin{equation}\label{eq:conds_DevSur2}
	\int_{0}^{L_L} \det (\zetavec_U(s_u(s_w)), \zetavec_W(s_w), \mbold{g}) ds_w = 0.
\end{equation}
Next, consider a “fuzzy” condition for a brassiere cup. As mentioned, the upper line has a connection point as shown in \rfig{fig:aboutCP}. But it is typically given as a fuzzy condition in the design process. This can lead to an unexpected error in the optimization problem. Therefore, we propose the following equation to deal with this fuzzy condition $ y \simeq Y $:
\begin{equation}\label{eq:FuzzyEq}
C(y,Y) = k_1 \exp( k_2(y-Y)^2 )
\end{equation}
where $ k_1 $ and $ k_2 $ are the variables to adjust the range that satisfies this condition. By adding this equation to the objective function, the fuzzy condition can be handled. Here, we assume that the position $ \mbold{X}_C $ to connect the upper line and the shoulder strap is given. Then the objective function $ V $ is described as
\begin{equation}\label{eq:ObjectFunc}
V = \Lambda(\mbold{D}) + \sum_{i=0}^{2} C(\mbold{x}_U \cdot \mbold{e}_i , \mbold{X}_C \cdot \mbold{e}_i)
\end{equation}
where $\mbold{e}_0 $ ,$\mbold{e}_1 $ and $\mbold{e}_2 $ are represented as unit vectors of $ x $,$ y $ and $ z $-axis. Solving this optimization under these constraints can provide the shape of the brassiere cup to fit the data points of a breast.

@@

\begin{equation}\label{eq:U_eq}
\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\omega_{\eta_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\upsilon_U} \cdot  \mbold{e}(s_w)  \end{array} \right]
\end{equation}
where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods. \chcolor{Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system, $ \mbold{a}_R $ be a set of the vectors $ [\mbold{a}_{\omega_{\xi_R}} \;\; \mbold{a}_{\omega_{\eta_R}} \;\; \mbold{a}_{\upsilon_R}] $ and  $ \mbold{a}_U $ be a set of the vectors $ [\mbold{a}_{\omega_{\xi_U}} \;\; \mbold{a}_{\omega_{\eta_U}} \;\; \mbold{a}_{\upsilon_U}] $.}
From above, the objective function, which is expressed as \req{eq:ObjectFunc}, and the geometric constraints, which are expressed as  \req{eq:conds_endp1,eq:conds_endp2,eq:conds_DevSur1,eq:conds_DevSur2} are described by the following total parameter vector 
\begin{equation}\label{eq:TotalCoefs}
\mbold{a}_{\mathrm{all}} = \left[ \begin{array}{cccc}
\mbold{a}_R & \mbold{a}_U & \mbold{\Phi}_{R0} &\mbold{\Phi}_{U0} 
\end{array}\right].
\end{equation}

@@

\section*{SIMULATION AND VERIFICATION}
To demonstrate the utility of our method, we conducted simulations and a verification. 
\subsection*{Simulation Example}
For simulation, the infinitesimal rotational ratios vector   of the wire line is given as
\begin{equation}\label{eq:vrf_omgW}
	\mbold{\omega}_W = \left[ \begin{array}{ccc}
	0 & 2.91 & 0
	\end{array}\right]^\mathrm{T}, 
\end{equation}
while the connection point $ \mbold{X}_C $ is \chcolor{given in case (1) and (2) as} 
\begin{equation}\label{eq:givenXc}
	\mbold{X}_C = \left[ \begin{array}{ccc}
	0 & 0.34 & 0.34
	\end{array}\right]^\mathrm{T},
\end{equation}
We prepared tho examples of the simulation. Case (1) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}. Case (2) is a point cloud on a sphere whose radius is set on R by a uniform random number. The simulations aim to confirm that the propose method recreates a given shape and to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface.

\rfig{fig:ObtainedSurfaceDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line. Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.  \rfig{fig:ObtainedSurfaceDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively.
Next, a uniform random number was generated by numpy.random() of Python. \rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2). \rtab{tbl:error and calc_Example} shows the error and calculation time of case(1) and (2).
\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|} \hline
		-& Error & Time[sec] \\ \hline
		case(1) & 0.10 & 1802 \\ \hline
		case(2) & 0.12 & 740 \\ \hline
	\end{tabular}
	\caption{The error and calculation time of our proposed method in case(1) and (2).}
	\label{tbl:error and calc_Example}
\end{table}
For this result, we confirm that our proposed method can recreate a given shape as a two-piece brassire cup and approximate an undevelopable surface.

\subsection*{Experimental Verification}
For confirming the verification, we measured a breast shape of the torso, which is a typical breast shape, and apply our proposed method to it. A wire line is the same as \req{eq:vrf_omgW}, and the connection point is given as 
\begin{equation}\label{eq:givenXc2}
	\mbold{X}_C = \left[ \begin{array}{ccc}
	0.2 & 0.41 & 0.27
	\end{array}\right]^\mathrm{T}.
\end{equation}
In measured the entire shape of a torso, we used the measured point cloud that satisfies $ y \leq 0.2 $ as shown in \rfig{fig:Border}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\columnwidth]{./figure/Measure/SetLine.png}
	\caption{The border line to use a point cloud in the experiment.}
	\label{fig:Border}
\end{figure}  
\chcolor{The simulations aim to confirm that the propose method whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” .\rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data of experiments,  \rfig{fig:ObtainedSurfaceNDS2_Pat} shows the obtained pattern. In \rfig{fig:ObtainedSurfaceNDS2} and \rfig{fig:ObtainedSurfaceNDS2_Pat}, we set $ L_M = 72.8$. } \chcolor{\rtab{tbl:error and calc2} shows the error and calculation time of the experiment. From the result, we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.
Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.}
\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|} \hline
		Error & Time[sec] \\ \hline
		1.04& 1682 \\ \hline
	\end{tabular}
	\caption{The error and calculation time of the proposed method in experiment.}
	\label{tbl:error and calc2}
\end{table}

\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-x.png}
		\label{fig:zx-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromz-y.png}
		\label{fig:zy-DS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/DS/ObtainedRidgeLinefromx-y.png}
		\label{fig:xy-DS}
	}
	\caption{Obtained shape and input data points in Case(2)}
	\label{fig:ObtainedSurfaceDS}
\end{figure}
